Covariate analysis of CMC RNASeq data reprocessed with Star-HTSeq pipeline (DLPFC with TMM normlaisation)

### 2016-09-19 code/Rmd/CMC_DLPFC_StarAligned_TMM.Rmd
Minor modifications

knit2synapse::knitToFolderEntity(file = "./CMC_DLPFC_StarAligned_TMM.Rmd",
                                 parentId ="syn5569976",
                                 entityName = 'CMC - DLPFC - STAR Reprocessed - with TMM')
```

@@

# Add primary variable to the list (in case not chosen by iterative method)
postAdjustCovars = unique(c(postAdjustCovars, 'Dx'))

@@

p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC)) + geom_point() + xlim(c(-1,1))
p = p + geom_hline(yintercept = -log10(0.05), color = 'red') 
p = p + geom_vline(xintercept = log2(1.2), color = 'red') 
p = p + geom_vline(xintercept = -log2(1.2), color = 'red') 
p = p + facet_grid(.~Comparison, scales = 'fixed')
p
```
### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "CMC - DLPFC - STAR Reprocessed - with TMM", parentId = parentId)
CODE <- synStore(CODE)

>>>>

knit2synapse::knitToFolderEntity(file = "./CMC_DLPFC_StarAligned_TMM.Rmd",
                                 parentId ="syn5569976",
                                 entityName = 'DLPFC - STAR Reprocessed - with TMM')
```

@@

# Add primary variable to the list (in case not chosen by iterative method)
postAdjustCovars = unique(c('Dx', postAdjustCovars))

@@

p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC)) + geom_point() + xlim(c(-1,1))
p = p + geom_hline(yintercept = -log10(0.05), color = 'red') 
p = p + geom_vline(xintercept = log2(1.2), color = 'red') 
p = p + geom_vline(xintercept = -log2(1.2), color = 'red') 
p = p + facet_grid(.~Comparison, scales = 'fixed')
p
```
### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "DLPFC - STAR Reprocessed - with TMM", parentId = parentId)
CODE <- synStore(CODE)
